Looking at Non-Linear Dimension Reductions as Models in the Data Space

### 2025-03-17 paper.qmd
Updated the projectio plot with new function for PBMC3k

pbmc_proj_umap_model1_best <- projected_df |>
  ggplot(
    aes(
      x = proj1, 
      y = proj2)) +
  geom_segment(
    data = model_df, 
    aes(
      x = proj1_from, 
      y = proj2_from, 
      xend = proj1_to, 
      yend = proj2_to), 
    color = "#000000") +
  geom_point(
    #size = 0.5,
    alpha = 0.2,
    color = "#999999") +
  geom_segment(
    data=axes, 
    aes(x=x1, y=y1, xend=x2, yend=y2), 
    colour="grey70") +
  geom_text(
    data=axes,
    aes(x=x2, y=y2), 
    label=rownames(axes),
    colour="grey50",
    size = 3) +
  geom_path(
    data=circle, 
    aes(x=c1, y=c2), colour="grey70") +
  coord_fixed() +
  xlim(c(-0.65, 0.65)) +
  ylim(c(-0.65, 0.65)) +
  interior_annotation("b2", cex = 2)

@@

pbmc_proj_umap_model2_best <- projected_df |>
  ggplot(
    aes(
      x = proj1,
      y = proj2)) +
  geom_segment(
    data = model_df,
    aes(
      x = proj1_from,
      y = proj2_from,
      xend = proj1_to,
      yend = proj2_to),
    color = "#000000") +
  geom_point(
    #size = 0.5,
    alpha = 0.2,
    color = '#999999') +
  geom_segment(
    data=axes,
    aes(x=x1, y=y1, xend=x2, yend=y2),
    colour="grey70") +
  geom_text(
    data=axes,
    aes(x=x2, y=y2),
    label=rownames(axes),
    colour="grey50",
    size = 3) +
  geom_path(
    data=circle,
    aes(x=c1, y=c2), colour="grey70") +
  coord_fixed() +
  xlim(c(-1, 0.75)) +
  ylim(c(-1, 0.75)) +
  interior_annotation("b3", cex = 2)

>>>>

pbmc_proj_umap_model1_best <- plot_proj(
    projected_df = projected_df, 
    model_df = model_df, 
    axes = axes, 
    circle = circle, 
    point_param = c(1.5, 0.2, "#999999"), # size, alpha, color
    plot_limits = c(-0.65, 0.65), 
    title = "b2", 
    cex = 2, 
    is_category = FALSE)

@@

pbmc_proj_umap_model2_best <- plot_proj(
    projected_df = projected_df, 
    model_df = model_df, 
    axes = axes, 
    circle = circle, 
    point_param = c(1.5, 0.2, "#999999"), # size, alpha, color
    plot_limits = c(-1, 0.75), 
    title = "b3", 
    cex = 2, 
    is_category = FALSE)
```
